2-factor-Hull-White\_model\_calibration

### 2020-05-12 week3/Report.tex
Delete old conclusion

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_41_0.png}
    \end{center}
    { \hspace*{\fill} \\}
\section{Conclusion}
In this paper, we simulated correlated firm and share price paths. From this, we priced an up-and-out call option at 8.299 with a default-free risk profile, and at 8.281 for the CVA-adjusted price. Considering that the same parameters are used as the first submission, where the Black-Scholes-Merton model was used to arrive at a price of 5.697, we observe that both the default risk, the variable interest rate and local volatility have all added a premium to the option price. These conditions, which are more aligned to observed market conditions, gave a total increase of 45\% over the previously calculated price, with the default risk accounting for only 0.2\% of the difference. These results underline the importance of choosing the correct model and performing accurate calibration in order to calculate instrument prices.

We are well aware that Black-Scholes formula was derived under assumptions which might not hold in a real market, as an example, if the share price deviates from the geometric Brownian motion, then our estimates can be wrong by a big margin. Also, our Monte Carlo estimates are highly dependant on parameters such as firm value; if firm value is well above debt value and the volatility of the firm is low, the chance of default is really low.
\newpage
\section*{} \label{bibsection}

>>>>

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_41_0.png}
    \end{center}
    { \hspace*{\fill} \\}
\section{Conclusion}
In this paper, we simulated correlated firm and share price paths. From this, we priced an up-and-out call option at 8.299 with a default-free risk profile, and at 8.281 for the CVA-adjusted price. Considering that the same parameters are used as the first submission, where the Black-Scholes-Merton model was used to arrive at a price of 5.697, we observe that both the default risk, the variable interest rate and local volatility have all added a premium to the option price. These conditions, which are more aligned to observed market conditions, gave a total increase of 45\% over the previously calculated price, with the default risk accounting for only 0.2\% of the difference. These results underline the importance of choosing the correct model and performing accurate calibration in order to calculate instrument prices.
\newpage
\section*{} \label{bibsection}
